### 2016-09-30 notions.tex
proof of meta-theorem done

\begin{theorem}
Let $\setprim=(\Rep, \Qry)$ be a canonical data structure for which $\Rep$
has canonical representation
$(\Rep_1, \Rep_2, F)$. Then for ${\sf leak}(S) = |S|$ and
any attacker $A$, there is an attacker
$A'$ running in about the same time for which
\[\AdvPrivSS{\setprim,{\sf leak}}{A} \leq {\sf Adv}_F^{\rm PRF}(A'). \]
\end{theorem}
\begin{proof}
We define a simulator $\Sim$ as follows. On input $n$, $\Sim$ fixes
a set $S^*=\{e_1, \ldots, e_n\}$. It then computes $s_1,
\ldots, s_t \getsr \Rep_1(S^*)$, chooses a uniform key
$K \getsr \calK$, runs $\pubaux
\getsr \Rep_2(|S|, F_K(s_1), \ldots, F_K(s_t))$, and finally returns
$\pubaux$.

@@

For a given set $S$, define distribution $\mbox{{\sc Real}}_S$ as
\[ \{ (\pubaux, \privaux) \getsr \Rep(S) : \pubaux\},\]
and define distribution $\mbox{{\sf Ideal}}_S$ as
\[ \{ \pubaux \getsr \Sim(|S|) : \pubaux \}.\]
Our goal is to show that $\mbox{{\sc Real}}_S$ and $\mbox{{\sf Ideal}}_S$ are computationally
indistinguishable for any set~$S$. \jnote{I'm not quite sure how to elegantly do a proof
like this in the concrete setting.}\tsnote{I think you just follow the
sketch that I typeset for the Domain-Separated PRF scheme. (I'll embed
notes below, too.) The bound will be exactly what is there, shoudl be able to just cut-and-paste,
basically.  All that's needed, I think, is to do resource accounting
for $\Sim$ and the PRF-adversary~$B$.}
To do so, first note that we can express $\mbox{{\sc Real}}_S$ as the outcome of
the following experiment: \tsnote{I'd call this ``Game $G0$''...}
\begin{enumerate}
\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
\item $K \getsr \bits^n$.
\item $\pubaux \getsr \Rep_2(|S|, F_k(s_1), \ldots, F_k(s_t))$.
\item Return $\pubaux$.
\end{enumerate}

Now, consider a hybrid distribution $\hyb_S$ computed as follows:
\tsnote{...and this ``Game $G1$''...}
\begin{enumerate}
\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
\item $y_1, \ldots, y_t \leftarrow \bits^{\ell_{out}}$
\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_t)$.
\item Return $\pubaux$.
\end{enumerate}
It follows immediately from the fact that $F$ is a pseudorandom function (and efficiency
of $\Rep_2$) that $\hyb_S$ is computationally indistinguishable from $\mbox{{\sc Real}}_S$.
\tsnote{...and then it's clear that the difference between the
  probability of $G0 \outputs 1$ and $G1 \outputs 1$ is exactly the
  PRF advantage of~$B$, who simply uses it's oracle to simulate calls
  to $F_K$ prior to running $\Rep_2$...}
Next, consider the following distribution $\hyb'_S$:
\begin{enumerate}
\item $S^* := \{e_1, \ldots, e_n\}$, where $n = |S|$.
\item $s_1, \ldots, s_{t^*} \getsr \Rep_1(S^*)$.
\item $y_1, \ldots, y_{t^*} \leftarrow \bits^{\ell_{out}}$
\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_{t^*})$.
\item Return $\pubaux$.
\end{enumerate}
We claim that $\hyb'_S$ is identically distributed to $\hyb_S$. The follows immediately from the
observation that the distribution on $t$ (in $\hyb_S$) is identical to the distribution on~$t^*$
(in $\hyb'_S$) by definition
of what it means to be canonical.
\tsnote{...and it is clear that the distribution of everything is the
  same as in Game $G1$, so we are done. }

To complete the proof, we simply note that $\hyb'_S$ and $\mbox{{\sf Ideal}}_S$
are computationally indistinguishable, again relying on pseudorandomness of~$F$.
\end{proof}
\fixme{ ----The following is left only for cut-and-paste value---- }
\begin{theorem}\label{thm:ds-ss}
Fix $k,m,n>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S \in 2^\elts$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}[Proof (sketch). ] \todo{Move this sketch to be a proof
    of Jon's meta-result. Downgrade theorem to be a corollary of that
    result, the proof simply being a description of how $\Rep$
    decomposes into $\Rep_1$ and $\Rep_2$.}
Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\setprim_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.  When~$f=F_K$ then the simulation is perfect.  When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\overline{\setprim}_{\mathrm{ds}}}{A}$ where $\overline{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.  But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.  Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
\end{proof}
\fixme{ ----The above is left only for cut-and-paste value---- }

>>>>

\begin{theorem}
Let $\setprim=(\Rep, \Qry)$ be a canonical data structure for which $\Rep$
has canonical representation
$(\Rep_1, \Rep_2, F)$. Then for ${\sf leak}(S) = |S|$ and
any attacker $A$, there is an attacker
$A'$ running in about the same time for which
\[\AdvPrivSS{\setprim,{\sf leak}}{A} \leq {\sf Adv}_F^{\rm PRF}(A'). \]
\end{theorem}
\begin{proof}
We define a simulator $\Sim$ as follows. On input $n$, $\Sim$ fixes
a set $S^*=\{e_1, \ldots, e_n\}$. It then computes $s_1,
\ldots, s_t \getsr \Rep_1(S^*)$, chooses uniform values $y_1, \ldots, y_t \getsr \bool^{\ell_{out}}$,
and returns $\pubaux
\getsr \Rep_2(|S|, y_1, \ldots, y_t)$.

@@

Note that we can express $\Prob{\ExpPrivSSreal{\setprim}{A}=1}$ as the probability that $A$
outputs~1 in
the following experiment~$G0$: \jnote{BTW, in class when I do this stuff I usually
say ``game'' and then correct myself and say ``\ldots but if you want to get funded,
call it an experiment.'' (Some light humor while you work.)}
\begin{enumerate}
\item $S \getsr A$.
\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
\item $K \getsr \bits^n$.
\item $\pubaux \getsr \Rep_2(|S|, F_k(s_1), \ldots, F_k(s_t))$.
\item Return $A(\pubaux)$.
\end{enumerate}

Now, consider an experiment $G1$ in which computation is done as follows:
\begin{enumerate}
\item $S \getsr A$.
\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
\item $y_1, \ldots, y_t \leftarrow \bits^{\ell_{out}}$
\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_t)$.
\item Return $A(\pubaux)$.
\end{enumerate}
It is immediate that the difference between the probability that $A$ outputs~1 in
$G1$ and the probability that it outputs~1 in
$G0$ is bounded by ${\sf Adv}_F^{\rm PRF}(A')$, where $A'$ performs the
obvious simulation.

Next, consider the following experiment $G2$:
\begin{enumerate}
\item $S \getsr A$.
\item $S^* := \{e_1, \ldots, e_n\}$, where $n = |S|$.
\item $s_1, \ldots, s_{t^*} \getsr \Rep_1(S^*)$.
\item $y_1, \ldots, y_{t^*} \leftarrow \bits^{\ell_{out}}$
\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_{t^*})$.
\item Return $A(\pubaux)$.
\end{enumerate}
We claim that the probability with which $A$ outputs~1 in $G2$ is \emph{identical} to the
probability with which it outputs~1 in $G1$.
The follows immediately from the
observation that the distribution on $t$ (in $G1$) is identical to the distribution on~$t^*$
(in $G2$) by definition
of what it means to be canonical, and it is clear that the distributions of everything
else are the same as well.

One can observe that $G2$ is identical to the following experiment:
\begin{enumerate}
\item $S \getsr A$.
\item $\pubaux \getsr \Sim(|S|)$.
\item Return $A(\pubaux)$.
\end{enumerate}
Moreover, the probability with which $A$ outputs~1 in this experiment is
precisely $\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1}$.
This completes the proof.
\end{proof}

%\fixme{ ----The following is left only for cut-and-paste value---- }
%\begin{theorem}\label{thm:ds-ss}
%Fix $k,m,n>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S \in 2^\elts$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ such that, for any adversary~$A$
%\[
%\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
%\]
%where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
%\end{theorem}
%\begin{proof}[Proof (sketch). ] \todo{Move this sketch to be a proof
%    of Jon's meta-result. Downgrade theorem to be a corollary of that
%    result, the proof simply being a description of how $\Rep$
%    decomposes into $\Rep_1$ and $\Rep_2$.}
%Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\setprim_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.  When~$f=F_K$ then the simulation is perfect.  When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\overline{\setprim}_{\mathrm{ds}}}{A}$ where $\overline{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.  But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.  Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
%\end{proof}
%\fixme{ ----The above is left only for cut-and-paste value---- }
